\section{Paper Organization}

This paper has been organized as a bottom up approach to the formation
of our system.
We have elected to explain the operation in this way because the system
has been engineered to be largely ignorant of the operations at layers
above and below a given primitive.
Thus, our system allows application logic to change while preserving
the consensus mechanisms.
The system also allows the consensus mechanism to be changed while
preserving the application logic.
Due to this design, the system is most easily digested by building it
in layers of complexity.

The first sections pertain to the encoding of messages within the
system.
The next section addresses the operation of transaction processing.
The section following gives insight into the synchronization and how
history may be safely pruned from the system.
Following these sections the consensus algorithm itself is covered in
full detail.
The networking stack is then addressed to describe the communication
between nodes, based on the consensus algorithm.
Finally, the economics of the system are covered.

The treatment of these topics is not performed in a technical manner in
the body of the paper proper, aside from the proof of the consensus
algorithm.
This choice was made because the consensus proof is far less technical
than the cryptography of the system, and may be understood by the
intended audience of this paper.
The formal treatment of cryptographic operation has been performed in
the technical addendum of this paper; see Appendix~\ref{sec:tech_crypto}.
